Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-02-22 RR_manuscript/Draft_RR.Rmd
:memo: edit RR

## The data set - The prosody of redundant modifiers

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g. *a blue banana* vs *a yellow banana*)?
We are interested in the acoustic profile of referring expressions.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy [@grice1975logic].
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

>>>>

## The data set: The acoustic properties of redundant modifiers

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g. the atypical *a blue banana* vs the typical *a yellow banana*)?
More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy [@grice1975logic].
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
